Determinism, Complexity, and Predictability in Computer Performance

### 2014-07-28 related.tex
update boffetta stuff

More closely related is the work by Boffetta \emph{et
  al.}~\cite{boffetta02}, who investigate the scaling behavior of
finite-size Lyapunov exponents (FSLE) and $\epsilon$-entropy for a
wide variety of deterministic systems with known dynamics.  While the
scaling of these measures acts as a general proxy for predictability
bounds, this approach differs from our work in a number of fundamental
ways.  First, we focus on real-world time-series data, where one does
not necessarily have the ability to perturb or otherwise interact with
the system of interest, nor can one obtain or manufacture the
(possibly large) number of points that might be needed to estimate the
$\epsilon$-entropy for small $\epsilon$.  Second, we tie
information---in the form of the weighted permutation
entropy---directly to prediction error via MASE values.  Though FSLE
and $\epsilon$-entropy allow for the comparison of predictability
between systems, they do not directly provide an estimate of
prediction error.  \alert{Finally, our approach also holds for
  \emph{stochastic} systems, where the computation of FTLEs makes no
  sense and/or doesn't reflect predictability.  [[I remember someone
      saying this but didn't see it here, so I added it.  Boffetta et
      al. just do dynamical systems, yes?  And lambda of a stochastic
      system wouldnt' make sense, yes?]]}

>>>>

More closely related is the work by Boffetta \emph{et
al.}~\cite{boffetta02}, who investigate the scaling behavior of
finite-size Lyapunov exponents (FSLE) and $\epsilon$-entropy for a
wide variety of deterministic systems with known dynamics.  While the
scaling of these measures acts as a general proxy for predictability
bounds, this approach differs from our work in a number of fundamental
ways.  First, we focus on real-world time-series data, where one does
not necessarily have the ability to perturb or otherwise interact with
the system of interest, nor can one obtain or manufacture the
(possibly large) number of points that might be needed to estimate the
$\epsilon$-entropy for small $\epsilon$.  Second, we tie information
---in the form of the weighted permutation entropy---directly to
prediction error via MASE values.  Though FSLE and $\epsilon$-entropy
allow for the comparison of predictability between systems, they do
not directly provide an estimate of prediction error.  Finally, our
approach also holds for \emph{stochastic} systems, where the
computation of FSLEs makes no sense and/or doesn't reflect
predictability, and Boffetta et al.'s analysis requires knowledge of
the noise and its interaction with the system.
